---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---
In this page, I am trying to make plots using plotly. 

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(plotly)
library(p8105.datasets)

data(rest_inspec)
inspect = rest_inspec
```

# Data Clean

First let's clean and tidy data. Since the dataset is too large, I will only focus on Chinese restaurants. 

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
inspect |> 
  janitor::clean_names() 
chinese_restaurants = subset(inspect, cuisine_description == "Chinese") |> 
  drop_na(score) |> 
  drop_na(boro)
```

# Bar Plot

Then I want to check those restaurants with more than 50 inspections using a bar plot. 

```{r}
inspection_counts = chinese_restaurants |>
  group_by(dba) |>
  summarise(inspection_count = n())

filtered_inspection_counts = inspection_counts |>
  filter(inspection_count > 50) |>
  arrange(inspection_count) |>
  mutate(dba = fct_inorder(dba))

plot_ly(filtered_inspection_counts, x = ~dba, y = ~inspection_count, type = 'bar') |>
  layout(title = 'Number of Inspections per Restaurant (More than 50 Inspections)',
         xaxis = list(title = 'Restaurant', tickangle = -45),
         yaxis = list(title = 'Number of Inspections'))

```

# Box Plot

Then I make a boxplot of the score of different boroughs in New York. 

```{r}
restaurant_score = chinese_restaurants |>
  select(boro, score) |>
  filter(!is.na(score))

plot_ly(restaurant_score, y = ~score, color = ~boro, type = 'box') |>
  layout(title = 'Score Distribution by Borough',
         yaxis = list(title = 'Score'),
         xaxis = list(title = 'Borough'))
```

# Line Plot

Then I make a line plot of the restaurant which has the most inspections and show how its score changes over those years. 

```{r}
no_1_chinese_data = chinese_restaurants |>
  filter(grepl("NO. 1 CHINESE RESTAURANT", dba)) |>
  arrange(as.Date(grade_date, format = "%m/%d/%Y")) |>
  mutate(score = as.numeric(score))

plot_ly(no_1_chinese_data, x = ~grade_date, y = ~score, type = 'scatter', mode = 'lines+markers',
                     line = list(shape = "spline")) |>
  layout(title = 'Score Changes Over Time for No. 1 Chinese Restaurant',
         xaxis = list(title = 'Date'),
         yaxis = list(title = 'Score'))
```

